---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```


###Binomial

The binomial distribution is the discrete probability distribution of the number of successes in n independent trials.  

The package `binomial` allows users to calculate the probability for a random variable with a binomial distribution. It also displays and visualizes the binomial probability distribution and the binomial cumulative distribution given certain the number of trials done and the probability of success for a given trial.  

###Creating a random variable

We first create a random variable using the function `bin_variable()`. This function takes in two arguments:  1) `trials` -- the number of trials  
2) `prob` -- the probability of success in a given trial  
and will print these parameters in an easy-to-read manner.  

For example:
```{r}
bin <- bin_variable(trials = 10, prob = 0.3)
bin
```

Here, bin is a `bin_var` object.  


###Summary of the random variable
Users can also find out the mean, variance, mode, skewness and kurtosis of this random variable at once simply by calling the function `summary` on a `bin_var` object.   

For example:
```{r}
summary(bin)
```


###Individual measurements
Alternatively, users can find out about each individual measurements by using their respective individual functions. All the functions discussed below takes in two arguments: 
1) `trials` -- the number of trials   
2) `prob` -- the probability of success in a given trial    

Users can call `bin_mean()` to calculate the expected value or mean of the binomial distribution. This is the expected number of successes in n trials.  

for example:
```{r}
bin_mean(trials = 10, prob = 0.3)
```

Next, users can call `bin_variance()` to find the variance of the binomial distribution. Variance is the square of the standard deviation of the distribution, which is a measure of the spread of the distribution.  

for example:
```{r}
bin_variance(trials = 10, prob = 0.3)
```

User can call `bin_mode()` to find the mode of the distribution, or the most likely number of success in n independent trials.  

for example:
```{r}
bin_mode(trials = 10, prob = 0.3)
```

Users can call the function `bin_skewness()` to find skewness of the distribution. Skewness is a measure of the asymmetry of the probability distribution of a random variable about its mean. Skewness describes the shape of the probability distribution.   

for example:
```{r}
bin_skewness(trials = 10, prob = 0.3)
```

Lastly, users can call the function `bin_kurtosis()` to find the kurtosis of the distribution. Kurtosis is a measure of the “tailedness” of the probability distribution of a random variable. Kurtosis is a descriptor of the shape of the probability distribution.   

for example:
```{r}
bin_kurtosis(trials = 10, prob = 0.3)
```

###Combinations
Users can find out the number of combinations in which k successes can occur in n trials by calling the function `bin_choose()`. This function takes in two arguments:
1) `n` -- the number of trials  
2) `k` -- the number of successes  

for example:
```{r}
bin_choose(n = 5, k = 2)
```

###Binomial Probability
Users can immediately calcualte the probability of getting k success in n trials given p probability of success in each trial by calling the function `bin_probability()`. This function takes in three arguments:
1) `success` -- the number of success  
2) `trials` -- the number of trials  
3) `prob` -- the probability of success in each trial

for example:
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

###Binomial Probability Distribution
Users can get the binomial probability distribution in the form of a table, which has the number of success in a column and the probability of each success in another column, by calling the function `bin_distribution()`. This function takes in two arguments:
1) `trials` -- the number of trials   
2) `prob` -- the probability of success in a given trial

This creates a `bindis` object.

for example:
```{r}
dis <- bin_distribution(trials = 5, prob = 0.5)
dis
```

Users can also visualize this probability distribution in a barplot format by calling the function `plot()` on the 

for example:
```{r}
plot(dis)
```

###Binomial Cumulative Distribution
Users can get the binomial probability distribution along with the cumulative distribution in the form of a table, which has the number of success in a column, the probability of each success in the second column, and the probability of getting at most that number of success in the third column, by calling the function `bin_cumulative()`.

This function takes in two arguments:
1) `trials` -- the number of trials   
2) `prob` -- the probability of success in a given trial

This creates a `bincum` object.

```{r}
dis1 <- bin_cumulative(trials = 5, prob = 0.5)
dis1
```

Users can also visualize the cumulative distribution in a barplot format by calling the function `plot()` on the `bincum` object created.

for example:
```{r}
plot(dis1)
```




